C/O and Snowline Locations in Protoplanetary Disks: The Effect of Radial Drift and Viscous Gas Accretion

### 2015-10-21 tex/draft/ms_final_revised.tex
update

\begin{figure}[h!]
\centering
\includegraphics[width=0.55\textwidth]{C_O_ratio_passive_active_disk_many_colorbar_complete_new.pdf}
%\vspace{-0.5in}
\caption{Estimated C/O ratio in gas (solid lines) and in dust (dashed lines) for an irradiated disk (top panel), an evolving disk (middle panel) and a viscous disk (bottom panel).
%, for the range of particle sizes that desorb at a fixed distance regardless of their initial location in the disk. 
The particle size increases from 0.001 cm to $\sim$700 cm as indicated by the color bar. The horizontal dotted line represents the stellar value of 0.54. The black lines represent the C/O ratio in gas (solid black line) and dust (dashed black line) for a static disk, with the temperature profile given by Equation (\ref{eq:diskT}) for the top two panels and by Equation (\ref{eq:activeT}) for the bottom panel. 
%The snowline location moves inward as the particle size increases. 
The curves exterior to the static snowline represent desorption distances in the absence of readsorption.  %Taking  readsorption into account, the snowlines for these particle sizes are in fact coincident with the static snowline. 
For both the evolving and the viscous disk, the movement of desorbed CO$_2$ gas inside the CO$_2$ snowline, and of desorbed CO$_2$ and H$_2$O gas inside the H$_2$O snowline due to gas accretion will increase the amount of oxygen gas inside the respective snowlines and thus reduce the gas C/O ratio, as shown by the arrows.}
%, with the decrease more significant interior to the H$_2$O snowline.}
\label{fig:CO_ratio}
\end{figure}

@@

Figure \ref{fig:CO_ratio} shows the estimated C/O ratio in gas and dust as a function of semimajor axis for an irradiated disk, an evolving disk, and a viscous disk, under the simplifying assumption that the abundance relative to hydrogen for each volatile is \textbf{initially} fixed, so that drift and accretion affect only the locations of the snowlines. We use the relative number densities of C and O in their different molecular forms (H$_2$O, CO$_2$ and CO) from Table 1 of \citet{oberg11}.  Snowline locations correspond to $r_{\rm des}$ in Figure \ref{fig:snowlines}, representing the location at which particles desorb in the absence of readsorption.  The C/O ratio for a static disk, where desorption and readsorption balance \citep{hollenbach09}, is shown as a guideline. We note that the true snowline for particles with $r_{\rm des}$ outside the static snowline is the static snowline itself---curves plotted at larger distances are not true snowlines.

@@

Figure \ref{fig:CO_ratio} plots snowline curves for particle sizes less than $\sim$ 7m.  In the outermost disk, H$_2$O, CO$_2$, and CO all solidify.  Hence, relative drift across the CO snowline can alter only the abundances of volatiles between the CO$_2$ and CO snowlines, but not the C/O ratio in this region.  Interior to the CO$_2$ snowline, however, relative drift is important. 
We have found that the largest drifting particles in our model ($\sim$7 m) drift faster than the gas at both the H$_2$O and CO$_2$ snowlines. We thus conclude that the C/O ratio interior to the H$_2$O and CO$_2$ snowlines in our evolving and viscous disks will be lower than in the static disk, due to the additional oxygen added to the gas by desorbing H$_2$O and CO$_2$.  For these particle sizes, our calculated C/O ratio is an upper limit,  as indicated by the arrows in Figure \ref{fig:CO_ratio}.

>>>>

\begin{figure}[h!]
\centering
\includegraphics[width=0.55\textwidth]{C_O_ratio_passive_active_disk_many_colorbar_complete_new2.pdf}
%\vspace{-0.5in}
\caption{Estimated C/O ratio in gas (solid lines) and in dust (dashed lines) for an irradiated disk (top panel), an evolving disk (middle panel) and a viscous disk (bottom panel).
%, for the range of particle sizes that desorb at a fixed distance regardless of their initial location in the disk. 
The particle size increases from \textbf{$\sim$0.05 cm} to $\sim$700 cm as indicated by the color bar. The horizontal dotted line represents the stellar value of 0.54. The black lines represent the C/O ratio in gas (solid black line) and dust (dashed black line) for a static disk, with the temperature profile given by Equation (\ref{eq:diskT}) for the top two panels and by Equation (\ref{eq:activeT}) for the bottom panel. 
%The snowline location moves inward as the particle size increases. 
%The curves exterior to the static snowline represent desorption distances in the absence of readsorption.  %Taking  readsorption into account, the snowlines for these particle sizes are in fact coincident with the static snowline. 
For both the evolving and the viscous disk, the movement of desorbed CO$_2$ gas inside the CO$_2$ snowline, and of desorbed CO$_2$ and H$_2$O gas inside the H$_2$O snowline due to gas accretion will increase the amount of oxygen gas inside the respective snowlines and thus reduce the gas C/O ratio, as shown by the arrows.}
%, with the decrease more significant interior to the H$_2$O snowline.}
\label{fig:CO_ratio}
\end{figure}

@@

Figure \ref{fig:CO_ratio} shows the estimated C/O ratio in gas and dust as a function of semimajor axis for an irradiated disk, an evolving disk, and a viscous disk, under the simplifying assumption that the abundance relative to hydrogen for each volatile is \textbf{initially} fixed, so that drift and accretion affect only the locations of the snowlines. We use the relative number densities of C and O in their different molecular forms (H$_2$O, CO$_2$ and CO) from Table 1 of \citet{oberg11}.  Snowline locations correspond to $r_{\rm des}$ in Figure \ref{fig:snowlines}, representing the location at which particles desorb in the absence of readsorption.  The C/O ratio for a static disk, where desorption and readsorption balance \citep{hollenbach09}, is shown as a guideline. We note that the true snowline for particles with $r_{\rm des}$ outside the static snowline is the static snowline itself---\textbf{thus only particles with initial sizes larger than $\sim$0.05 cm are plotted in the three panels, as particles that form snowlines at larger distances (cf. Figure \ref{fig:snowlines}) are not true snowlines}.

@@

Figure \ref{fig:CO_ratio} plots snowline curves for particle sizes \textbf{$\sim0.5$ cm $\lesssim $s$ \lesssim$ 7m}.  In the outermost disk, H$_2$O, CO$_2$, and CO all solidify.  Hence, relative drift across the CO snowline can alter only the abundances of volatiles between the CO$_2$ and CO snowlines, but not the C/O ratio in this region.  Interior to the CO$_2$ snowline, however, relative drift is important. 
We have found that the largest drifting particles in our model ($\sim$7 m) drift faster than the gas at both the H$_2$O and CO$_2$ snowlines. We thus conclude that the C/O ratio interior to the H$_2$O and CO$_2$ snowlines in our evolving and viscous disks will be lower than in the static disk, due to the additional oxygen added to the gas by desorbing H$_2$O and CO$_2$.  For these particle sizes, our calculated C/O ratio is an upper limit,  as indicated by the arrows in Figure \ref{fig:CO_ratio}.
